Project Light

### 2015-09-03 paper/paper.tex
add bib style, add Conclusion and Future Work first version, simplify bib file

As the android timer that triggers the bit "emission" cannot be too early but in fact tends to be a little late (cite android real time paper), the time at which the mote reads a bit is not in the middle of a period as suggested by Figure~\ref{fig:read_a_bit}.
It is at the very end of a period to maximize error avoidance due to "timer-lateness".

@@

As seen in (code example), calls to the driver that are being issued before the key material initialization are actually being canceled right now, but should eventually just be delayed and reissued once the initialization was finished.
Including the light app on a mote automatically redefines \textit{NETSTACK\_CONF\_LLSEC} to point to our link layer driver wrapper (and no further configuration needs to be done?).

@@

\begin{itemize}
	\item bidirectional communication using the LEDs of the mote (and maybe camera)
	\item 802.15.4 dongle to verify transmission (and do further initialization)
	\item initialize several mote together, separate synchronization and data sending
\end{itemize}

>>>>

As the android timer that triggers the bit "emission" cannot be too early but in fact tends to be a little late\cite{mongia2010reliable}, the time at which the mote reads a bit is not in the middle of a period as suggested by Figure~\ref{fig:read_a_bit}.
It is at the very end of a period to maximize error avoidance due to "timer-lateness".

@@

As seen in (code example), calls to the driver that are being issued before the key material initialization are actually being canceled right now, but should eventually just be delayed and reissued once the initialization was finished.
Including the light app on a mote automatically redefines \textit{NETSTACK\_CONF\_LLSEC}\footnote{This global constant defines the link layer driver that is used by the mote.} to point to our link layer driver wrapper (and no further configuration needs to be done?).

@@

In this paper, we presented a secure method for IoT-device initialization by transmitting initial keying material via light.
It is mainly targeted at private users and can easily be executed having no technical background at all.

Future work should target the further automation of the presented process, by establishing a bidirectional communication.
Using its camera the mobile phone could detect the current LED-state of the mote and react accordingly, e.g. start the data transmission or restart the whole process.
This would also make it easier to initalize several motes at once, which because of lack of synchronization is currently quite tedious.

User-friendliness should be prioritized as success and adoption of this presented additional security measure will greatly benefit from it.
